Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Text wrapping
A little cleanup

\begin{figure}[ht]
\centering
\includegraphics[width=0.7\textwidth]{figures/McMasters-Henderson-1980}
\caption{Airfoil lift to drag ratio as a function of Reynolds number, from
\cite{McMasters1980}.}
\label{fig:McMasters}
\end{figure}

@@

Chamorro et al. \cite{Chamorro2012} showed that turbulence statistics in an AFT
wake became
$Re$-independent at $Re_D \approx 1 \times 10^5$, and that mean velocity
profiles became $Re$-independent slightly earlier at $Re_D \approx 5 \times
10^4$.
\todo[inline]{What was Chamorro's blade chord Re?}
\section{Experimental Setup}

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{figures/turbine}
\caption{UNH-RVAT turbine model. Turbine blades and struts made from NACA 0020
profiles with 0.140 m chord. Note that the upper and lower mounting
flanges have been excluded as these were included in the tare drag
measurements.}
\label{fig:turbine}
\end{figure}

>>>>

\includegraphics[width=0.7\textwidth]{figures/McMasters-Henderson-1980}

\caption{Airfoil lift to drag ratio as a function of Reynolds number, from
\cite{McMasters1980}.}

\label{fig:McMasters}
\end{figure}

@@

Chamorro et al. \cite{Chamorro2012} showed that turbulence statistics in an AFT
wake became $Re$-independent at $Re_D \approx 1 \times 10^5$, and that mean
velocity profiles became $Re$-independent slightly earlier at $Re_D \approx 5
\times 10^4$.

\todo[inline]{What was Chamorro's blade chord Re?}

\section{Experimental Setup}

@@

\includegraphics[width=0.4\textwidth]{figures/turbine}

\caption{UNH-RVAT turbine model. Turbine blades and struts made from NACA 0020
    profiles with 0.140 m chord. Note that the upper and lower mounting flanges have
    been excluded as these were included in the tare drag measurements.}

\label{fig:turbine}
\end{figure}
